Arrows for Parallel Computations

### 2017-12-14 paper/content/utilityFunctions.tex
added clarification for (>>>) being hosted on Category in Standard GHC
minor

In Fig.~\ref{fig:profunctorArrow} we show how specific Profunctors can be turned into Arrows.

@@

instance (Category p, Strong p, Choice p) => ArrowChoice p where
  left = left'
\end{code}
\caption{Profunctors as Arrows}
\footnote{for additional information on the typeclasses see: \url{https://hackage.haskell.org/package/profunctors-5.2.1/docs/Data-Profunctor.html}}}
\label{fig:profunctorArrow}
\end{figure}

@@

instance (Trans a) => Future RemoteData a (Conf a) where
    put _ = put'
    get _ = get'

>>>>

In Fig.~\ref{fig:profunctorArrow} we show how specific Profunctors can be turned into Arrows. Note that in Standard GHC |(>>>)| has the type |(>>>) :: Category cat => cat a b -> cat b c -> cat a c| and is therefore not part of the |Arrow| typeclass.

@@

instance (Category p, Strong p, Choice p) => ArrowChoice p where
  left = left'
\end{code}
\caption{Profunctors as Arrows}
\footnote{for additional information on the typeclasses see: \url{https://hackage.haskell.org/package/profunctors-5.2.1/docs/Data-Profunctor.html} and \url{https://hackage.haskell.org/package/base-4.9.1.0/docs/Control-Category.html}}
\label{fig:profunctorArrow}
\end{figure}

@@

instance (Trans a) => Future RemoteData a Conf where
    put _ = put'
    get _ = get'
